---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF SS24"
author: "Dominik Stodola (12612007)"
date: "`r Sys.Date()`"
output: distill::distill_article
---


## Exercise 1: Initializing git (4 Points)

### Subtask d) 

**Strengths:**

1. Very hard to lose files with git

2. Great for collaboration


**Weaknesses:**

1. Not good for storing data

2. History takes up file space



## Exercise 2: Putting your Repository on GitHub (3.5 Points)

### Subtask a) 

**Link to repository:** https://github.com/DSt1999/exeRcise-sheet-3.git



## Exercise 3: Baby-Names in Munich (3.5 Points)


### Subtask b)


```{r}
library(readr)
library(tidyverse)

data_2023 <- read_csv("data/vornamen-muenchen-2023.csv")
data_2022 <- read_csv("data/open_data_portal_2022.csv")

class(data_2023$Anzahl)
class(data_2022$Anzahl)

data_2023 <- data_2023 %>%
  mutate(Anzahl = as.numeric(gsub("4 oder weniger", "4", Anzahl)))

data_2022 <- data_2022 %>%
  mutate(Anzahl = as.numeric(gsub("4 oder weniger", "4", Anzahl)))

class(data_2023$Anzahl)
class(data_2022$Anzahl)
```

**Explanation:** The column "Anzahl" initially had the type "character", because it contained the term "4 oder weniger", which was used to express the number of occurrences of a specific name being 4 or fewer. In order to covert the type to "numeric", the term "4 oder weniger" was substituted with the numeric value 4. The obvious repercussion is, that all instances where the count was actually fewer than 4 are now recorded as exactly 4, which is inaccurate.

### Subtask c)

```{r}
total_babies_2023 <- sum(data_2023$Anzahl, na.rm = TRUE)
total_babies_2022 <- sum(data_2022$Anzahl, na.rm = TRUE)

print(paste("Total number of babies in 2023:", total_babies_2023))
print(paste("Total number of babies in 2022:", total_babies_2022))
```

=> Year 2022 had the bigger baby boom.


### Subtask d)

```{r}
data_2023 <- data_2023 %>%
  mutate(year = 2023)

data_2022 <- data_2022 %>%
  mutate(year = 2022)

head(data_2023, 5)
head(data_2022, 5)
```


### Subtask e)

```{r}
data_combined <- bind_rows(data_2023, data_2022)

showCombined <- bind_rows(slice(data_combined, 1:5), slice(data_combined, 4290:4295))
print(showCombined)
```

### Subtask f)

```{r}
library(knitr)

names_combined <- data_combined %>%
  group_by(Vorname) %>%
  summarize(Total_Count = sum(Anzahl, na.rm = TRUE)) %>%
  arrange(desc(Total_Count))

top_10_names <- names_combined %>%
  top_n(10, Total_Count) %>%
  arrange(desc(Total_Count))

kable(top_10_names, caption = "Top 10 Most Popular Names Across 2022 and 2023")
```


## Exercise 4: Open Analysis (4 points)


### Subtask b)

```{r}
data_cancer <- read_csv("data/Five year cancer survival rates - Allemani et al..csv")

head(data_cancer, 10)
```


### Subtask c)

**Dataset Name:** Five year cancer survival rates

**Link:** https://github.com/owid/owid-datasets/tree/master/datasets/Five%20year%20cancer%20survival%20rates%20-%20Allemani%20et%20al.%20


### Subtask d)

**Research Question:** How have the five-year-survival rates for breast cancer developed over time across different countries?

**Relevancy**: The results can provide insight into potential medical and healthcare advancements


## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
