---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF SS24"
author: "Dominik Stodola (12612007)"
date: "`r Sys.Date()`"
output: distill::distill_article
---


## Exercise 1: Initializing git (4 Points)

### Subtask d) 

**Strengths:**

1. Very hard to lose files with git

2. Great for collaboration


**Weaknesses:**

1. Not good for storing data

2. History takes up file space



## Exercise 2: Putting your Repository on GitHub (3.5 Points)

### Subtask a) 

**Link to repository:** https://github.com/DSt1999/exeRcise-sheet-3.git



## Exercise 3: Baby-Names in Munich (3.5 Points)


### Subtask b)


```{r}
library(readr)
library(tidyverse)

data_2023 <- read_csv("data/vornamen-muenchen-2023.csv")
data_2022 <- read_csv("data/open_data_portal_2022.csv")

class(data_2023$Anzahl)
class(data_2022$Anzahl)

data_2023 <- data_2023 %>%
  mutate(Anzahl = as.numeric(gsub("4 oder weniger", "4", Anzahl)))

data_2022 <- data_2022 %>%
  mutate(Anzahl = as.numeric(gsub("4 oder weniger", "4", Anzahl)))

class(data_2023$Anzahl)
class(data_2022$Anzahl)
```

**Explanation:** The column "Anzahl" initially had the type "character", because it contained the term "4 oder weniger", which was used to express the number of occurrences of a specific name being 4 or fewer. In order to covert the type to "numeric", the term "4 oder weniger" was substituted with the numeric value 4. The obvious repercussion is, that all instances where the count was actually fewer than 4 are now recorded as exactly 4, which is inaccurate.

### Subtask c)

```{r}
total_babies_2023 <- sum(data_2023$Anzahl, na.rm = TRUE)
total_babies_2022 <- sum(data_2022$Anzahl, na.rm = TRUE)

print(paste("Total number of babies in 2023:", total_babies_2023))
print(paste("Total number of babies in 2022:", total_babies_2022))
```

=> Year 2022 had the bigger baby boom.


### Subtask d)

```{r}
data_2023 <- data_2023 %>%
  mutate(year = 2023)

data_2022 <- data_2022 %>%
  mutate(year = 2022)
```



## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.
b)  Download the dataset and track it in git.
c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: ...
-   Link: <https://github.com/owid/owid-datasets/>...

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.
e)  Use R to answer your chosen question.
f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
